---
title: "Untitled"
author: "Kate Tanabe"
date: "2023-03-27"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r}
setwd("C:/")
unlink(".RData")

knitr::opts_chunk$set(echo = TRUE)

mapTheme3 <- theme(plot.title =element_text(size=12),
                  plot.subtitle = element_text(size=8),
                  plot.caption = element_text(size = 6),
                  axis.line=element_blank(),
                  axis.text.x=element_blank(),
                  axis.text.y=element_blank(),
                  axis.ticks=element_blank(),
                  axis.title.x=element_blank(),
                  axis.title.y=element_blank(),
                  panel.background=element_blank(),
                  panel.border=element_blank(),
                  panel.grid.major=element_line(colour = 'transparent'),
                  panel.grid.minor=element_blank(),
                  legend.direction = "vertical", 
                  legend.position = "right",
                  plot.margin = margin(1, 1, 1, 1, 'cm'),
                  legend.key.height = unit(1, "cm"), legend.key.width = unit(0.2, "cm"))

plotTheme <- theme(
  plot.title =element_text(size=12),
  plot.subtitle = element_text(size=8),
  plot.caption = element_text(size = 6),
  axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
  axis.text.y = element_text(size = 10),
  axis.title.y = element_text(size = 10),
  # Set the entire chart region to blank
  panel.background=element_blank(),
  plot.background=element_blank(),
  #panel.border=element_rect(colour="#F0F0F0"),
  # Format the grid
  panel.grid.major=element_line(colour="#D0D0D0",size=.75),
  axis.ticks=element_blank())

plotTheme1 <- function(base_size = 12, title_size = 16) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = title_size, colour = "black"), 
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
   panel.grid.major = element_line("grey60", size = 0.1),
    panel.grid.minor = element_blank(),
   panel.border = element_rect(colour = "black", fill=NA, size=1),
    strip.background = element_rect(fill = "white", color = "NA"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=12),
    axis.text = element_text(size=10),
    plot.background = element_blank(),
    legend.background = element_blank(),
      #axis.line.y.left   = element_line(color = 'black', size =1),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"),
    strip.text.x = element_text(size = 14)
  )
}
  
plotTheme2 <- function(base_size = 12, title_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = title_size, colour = "black"), 
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
   panel.grid.major = element_line("grey60", size = 0.1),
    panel.grid.minor = element_blank(),
   panel.border = element_rect(colour = "black", fill=NA, size=1),
    strip.background = element_rect(fill = "white", color = "NA"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=12),
    axis.text = element_text(size=10),
    plot.background = element_blank(),
    legend.background = element_blank(),
      #axis.line.y.left   = element_line(color = 'black', size =1),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"),
    strip.text.x = element_text(size = 10)
  )
}

  mapTheme1 <- function(base_size = 12, title_size = 16) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = title_size,colour = "black"),
    plot.subtitle = element_text(size=8),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.line.y.left   = element_line(color = 'black', size =1),
    panel.grid.minor = element_blank(),
    strip.text.x = element_text(size = 14))
}
  
  
  
    mapTheme2 <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 12,colour = "black"),
    plot.subtitle = element_text(size=8),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.line.y.left   = element_line(color = 'black', size =1),
    panel.grid.minor = element_blank(),
    strip.text.x = element_text(size = 10),
    legend.direction = "vertical", 
                  legend.position = "right",
                  plot.margin = margin(1, 1, 1, 1, 'cm'),
                  legend.key.height = unit(1, "cm"), legend.key.width = unit(0.2, "cm"))
}

# load libraries
library(caret)
library(pscl)
library(plotROC)
library(pROC)
library(sf)
library(tidyverse)
library(knitr)
library(kableExtra)
library(FNN)
library(scales)
library(jtools)
library(viridis)
library(gridExtra)
library(raster)
library(rgdal)
  
colors <- c("#2F4858", "#1372A4", "#86BBD8", "#A8C686","#E75E15")

```

```{r}
fishnet_calgary <- st_read("C:/fishnet_calgary_data.geojson") %>%
  st_transform('EPSG:3780')

fishnet_calgary$slope <- as.factor(fishnet_calgary$slope)
fishnet_calgary$impervious <- as.factor(fishnet_calgary$impervious)
fishnet_calgary$inundation <- as.factor(fishnet_calgary$inundation)
fishnet_calgary$log_flow_acc <- log(fishnet_calgary$flow_acc)
fishnet_calgary$log_flow_acc <- ifelse(fishnet_calgary$log_flow_acc <= 0, 0, fishnet_calgary$log_flow_acc)
fishnet_calgary$log_parks_dist <- log(fishnet_calgary$parks_dist)
fishnet_calgary$log_water_dist <- log(fishnet_calgary$water_dist)
fishnet_calgary$log_parks_dist <- ifelse(fishnet_calgary$log_parks_dist <= 0, 0, fishnet_calgary$log_parks_dist)
fishnet_calgary$log_water_dist <- ifelse(fishnet_calgary$log_water_dist <= 0, 0, fishnet_calgary$log_water_dist)

fishnet_calgary.sf <- fishnet_calgary %>%
  st_as_sf()

```

```{r}
minneapolis <- 
  st_read("C:/Flood/City_Boundary.shp") %>%
  st_transform('ESRI:102271') 

mpls_fn <- 
  st_make_grid(minneapolis, 
               cellsize = 300,
               square = TRUE) %>%
  .[minneapolis] %>%
  st_sf() %>%
  mutate(uniqueID = rownames(.))

mpls_fn_centroid <- mpls_fn %>%
  st_centroid()

# DEM
dem_mpls <- read_sf("C:/Flood/fishnet_to_dem/dem.shp") %>%
  dplyr::select(-c(dem_Rowid, dem_UNIQUE, dem_ZONE_C, dem_COUNT, dem_AREA, geometry)) %>%
  dplyr::rename(dem = dem_MAX) %>%
  st_drop_geometry()


mpls_fn_dem <- left_join(mpls_fn, dem_mpls, by = "uniqueID")

mapA <- ggplot() +
  geom_sf(data = mpls_fn_dem, 
          aes(fill = dem),
          color=NA) +
  scale_fill_viridis_c(option = "G",
                       name = "Max elevation") +
  labs(title="Digital Elevation Model")+
  mapTheme1()

# Land Cover
#Land cover data was taken from Minnesota Land Cover Classification System (MLCCS) and cropped to the city of Minneapolis. Impervious versus pervious classification was completed in ArcGIS Pro.

lc_mpls <- read_sf("C:/Flood/fishnet_to_landclass/fishnet_to_landclass.shp") %>%
  dplyr::select(-c(land_class, land_cla_1, land_cla_2, land_cla_3, land_cla_4, geometry)) %>%
  dplyr::rename(pervious = land_cla_5) %>%
  st_drop_geometry()

lc_mpls$pervious <- ifelse(lc_mpls$pervious %in% c(0, 1), "pervious", "impervious")

mpls_fn_landcover <- left_join(mpls_fn, lc_mpls, by = "uniqueID")

mapB <- ggplot() +
  geom_sf(data = fishnet_minneapolis.sf, 
          aes(fill = as.factor(impervious)),
          color=NA) +
  scale_fill_viridis_d(option = "G",
                       name = "Factor",
                       labels = c("Pervious","Impervious"),) +
  labs(title="\nLand Cover")+
  mapTheme1()

# Distance - Parks
parks_mpls <- read_sf("C:/Flood/fishnet_to_parks/fishnet_to_parks.shp") %>%
  dplyr::select(-c(NEAR_FID)) %>%
  dplyr::rename(dist_parks = NEAR_DIST) %>%
  st_drop_geometry()

mpls_fn_parks<- left_join(mpls_fn, parks_mpls, by = "uniqueID")

mapC <- ggplot() +
  geom_sf(data = mpls_fn_parks, 
          aes(fill = dist_parks),
          color=NA) +
  scale_fill_viridis_c(option = "G",
                       name = "Distance (Meters)") +
  labs(title="Distance to \nNearest Park")+
  mapTheme1()

# Distance - Hydrology

water_mpls <- read_sf("C:/Flood/fishnet_to_water/fishnet_to_water.shp") %>%
  dplyr::select(-c(NEAR_FID)) %>%
  dplyr::rename(dist_water = NEAR_DIST) %>%
  st_drop_geometry()

mpls_fn_water <- left_join(mpls_fn, water_mpls, by = "uniqueID")

mapD <-ggplot() +
  geom_sf(data = mpls_fn_water, 
          aes(fill = dist_water),
          color=NA) +
  scale_fill_viridis_c(option = "G",
                       name = "Distance (meters)") +
  labs(title="Distance to Nearest\nHydrological Feature")+
  mapTheme1()

#slope

slope_mpls <- read_sf("C:/Flood/fishnet_to_slope/slope.shp") %>%
  dplyr::select(-c(slope_Rowi, slope_UNIQ, slope_ZONE, slope_COUN, slope_AREA, geometry)) %>%
  dplyr::rename(slope = slope_MEAN) %>%
  st_drop_geometry()

mpls_fn_slope <- left_join(mpls_fn, slope_mpls, by = "uniqueID")

mapE <- ggplot() +
  geom_sf(data = mpls_fn_slope, 
          aes(fill = slope),
          color=NA) +
  scale_fill_viridis_c(option = "G",
                       name = "Mean % Change") +
  labs(title="\nSlope")+
  mapTheme1()

# Flow Accumulation 
fac_mpls <- read_sf("C:/Flood/fishnet_to_fac/fac.shp") %>%
  dplyr::select(-c(fac_Rowid, fac_UNIQUE, fac_ZONE_C, fac_COUNT, fac_AREA, geometry)) %>%
  dplyr::rename(fac = fac_MAX) %>%
  st_drop_geometry()

mpls_fn_fac <- left_join(mpls_fn, fac_mpls, by = "uniqueID")

mapF <- ggplot() +
  geom_sf(data = mpls_fn_fac, 
          aes(fill = fac),
          color=NA) +
  scale_fill_viridis_c(option = "G",
                       name = "Max Flow") +
  labs(title="\nFlow Accumulation")+
  mapTheme1()

# Merging fishnet data together
mpls_fishnet <- merge(mpls_fn, dem_mpls, by="uniqueID")
mpls_fishnet <- merge(mpls_fishnet, slope_mpls, by="uniqueID")
mpls_fishnet <- merge(mpls_fishnet, fac_mpls, by="uniqueID")
mpls_fishnet <- merge(mpls_fishnet, parks_mpls, by="uniqueID")
mpls_fishnet <- merge(mpls_fishnet, water_mpls, by="uniqueID")
mpls_fishnet <- merge(mpls_fishnet, lc_mpls, by="uniqueID")

colnames(mpls_fishnet)[4] ="flow_acc"
mpls_fishnet$impervious <- ifelse(mpls_fishnet$pervious =='impervious',1,0)
mpls_fishnet$slope1 <- ifelse(mpls_fishnet$slope >= 5, 1, 0)
fishnet_minneapolis <- mpls_fishnet %>%
  dplyr::select(uniqueID, flow_acc, dist_water, dist_parks, impervious, slope1, geometry)
colnames(fishnet_minneapolis)[6] ="slope"
colnames(fishnet_minneapolis)[3] ="water_dist"
colnames(fishnet_minneapolis)[4] ="parks_dist"
fishnet_minneapolis$slope <- as.factor(fishnet_minneapolis$slope)
fishnet_minneapolis$impervious <- as.factor(fishnet_minneapolis$impervious)
fishnet_minneapolis.sf <- fishnet_minneapolis %>%
  st_as_sf()

fishnet_minneapolis$log_flow_acc <- log(fishnet_minneapolis$flow_acc)
fishnet_minneapolis$log_flow_acc <- ifelse(fishnet_minneapolis$log_flow_acc <= 0, 0, fishnet_minneapolis$log_flow_acc)
fishnet_minneapolis$log_parks_dist <- log(fishnet_minneapolis$parks_dist)
fishnet_minneapolis$log_water_dist <- log(fishnet_minneapolis$water_dist)
fishnet_minneapolis$log_parks_dist <- ifelse(fishnet_minneapolis$log_parks_dist <= 0, 0, fishnet_minneapolis$log_parks_dist)
fishnet_minneapolis$log_water_dist <- ifelse(fishnet_minneapolis$log_water_dist <= 0, 0, fishnet_minneapolis$log_water_dist)

```

# Exploraty Analysis & Feature Engineering
## Calgary Data
```{r}
ggplot() + 
 # geom_sf(data=fishnet_calgary.sf, fill = "#86BBD8") +
  geom_sf(data = fishnet_calgary.sf, aes(fill=as.factor(inundation)), color = "transparent")+
  scale_fill_manual(values = c("#A8C686", "#1372A4"),
                    labels = c("Not Flooded","Flooded"),
                    name = "") +
  labs(title="Observed Flooding in Calgary") +
  mapTheme1()
```

## Variables
```{r}
mapAA <- ggplot() +
  geom_sf(data = fishnet_calgary.sf, aes(fill = parks_dist), color=NA) +
  scale_fill_gradient(low =  "#86BBD8" , high = "#2F4858")+
  labs(title = "Distance to \nNearest Park", fill="Distance \n(meters)") + mapTheme1()


mapBB <- ggplot() +
  geom_sf(data = fishnet_calgary.sf, 
          aes(fill = as.factor(impervious)),
          color=NA) +
   scale_fill_manual(values = c("#86BBD8","#2F4858"), name = "Factor")+
  labs(title="Land Cover\n")+
  mapTheme1()

mapCC <- ggplot() +
  geom_sf(data = fishnet_calgary.sf, 
          aes(fill = parks_dist),
          color=NA) +
  scale_fill_gradient(low =  "#86BBD8" , high = "#2F4858",
                       name = "Distance (Meters)") +
  labs(title="Distance to Nearest Park")+
  mapTheme1()

mapDD <-ggplot() +
  geom_sf(data = fishnet_calgary.sf, 
          aes(fill = water_dist),
          color=NA) +
  scale_fill_gradient(low =  "#86BBD8" , high = "#2F4858",
                       name = "Distance (Meters)")
  labs(title="Distance to Nearest\nHydrological Feature")+
  mapTheme1()

mapEE <- ggplot() +
  geom_sf(data = fishnet_calgary.sf, 
          aes(fill = slope))+
 scale_fill_manual(values = c("#86BBD8","#2F4858"), name = "Factor")+
  labs(title="Slope\n")+
  mapTheme1()


mapFF <- ggplot() +
  geom_sf(data = fishnet_calgary.sf, 
          aes(fill = flow_acc),
          color=NA) +
  scale_fill_gradient(low =  "#86BBD8" , high = "#2F4858",
                       name = "Max Flow")
  labs(title="Flow Accumulation\n")+
  mapTheme1()

grid.arrange(ncol = 3, mapAA, mapCC, mapDD, mapEE, mapFF) 
#  labs(title="Minneapolis Variables")+
  mapTheme1()
```

```{r}
grid.arrange(ncol = 3, mapB, mapC, mapD, mapE, mapF) +
#  labs(title="Minneapolis Variables")+
  mapTheme1()

```


## Variable importance 
```{r}
fishnet_calgary.nogeom <- fishnet_calgary.sf %>%
  st_drop_geometry()

fishnet_calgary.nogeom %>%
  dplyr::select(inundation, water_dist, parks_dist, flow_acc) %>%
    gather(Variable, value, -inundation) %>%
    count(Variable, value, inundation) %>%
      ggplot(., aes(value, n, fill = inundation)) +   
        geom_bar(position = "dodge", stat="identity") +
        facet_wrap(~Variable, scales="free") +
        #scale_fill_manual(values = c("#E99191", "#E91C1C")) +
        labs(x="Inundation", y="Value",
             title = "") +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))

fishnet_calgary.nogeom %>%
    dplyr::select(inundation, slope, impervious) %>%
    gather(Variable, value, -inundation) %>%
    count(Variable, value, inundation) %>%
      ggplot(., aes(value, n, fill = inundation)) +   
        geom_bar(position = "dodge", stat="identity") +
        facet_wrap(~Variable, scales="free") +
       # scale_fill_discrete(values = c("#E99191")) +
        labs(x="Inundation", y="Value",
             title = "") +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Model Building
```{r}
#setting up data partition 

set.seed(634)
trainIndex <- createDataPartition(fishnet_calgary$inundation, p = .70,
                                  list = FALSE,
                                  times = 1)
calgaryTrain <- fishnet_calgary[ trainIndex,]
calgaryTest  <- fishnet_calgary[-trainIndex,]
```

```{r}
#building model 

options(scipen=999)

calgaryModel <- glm(inundation ~ log_flow_acc + log_water_dist + slope + log_parks_dist + impervious,
                    family="binomial"(link="logit"), data = calgaryTrain %>%
                      as.data.frame %>%
                      dplyr::select(-objectid, -geometry, -ldscmetric))
```


# Model Results
## Model summary 
```{r}
summary(calgaryModel)
```

## Histogram of Probability Predictions
```{r}
classProbs <- predict(calgaryModel, calgaryTest, type="response")

hist((classProbs), main = paste("Histogram of Predictions"), col = "#86BBD8", xlab = "Inundation Probability") + plotTheme1()
```

## Density of Probability Distribution
```{r}
testProbs <- data.frame(obs = as.numeric(calgaryTest$inundation),
                        pred = classProbs,
                        uniqueID = calgaryTest$uniqueID)
testProbs$obs <- ifelse(calgaryTest$inundation == 1, 1, 0)

ggplot(testProbs, aes(x = pred, fill=as.factor(obs))) + geom_density() +
  facet_grid(obs ~ .) + xlab("Probability") + ylab("Density") + geom_vline(xintercept = .38) +
  scale_fill_manual(values = c("#A8C686", "#86BBD8"),
                      labels = c("Not Flooded","Flooded"),
                                 name="") +
                      labs(title = "Distribution of Probabilities") + plotTheme1()
```

## Confusion Matrix 
#### might need to figure out different presentation for confusion matrix
Confusion matrix results table... 
```{r}
testProbs$predClass  = ifelse(testProbs$pred > .5 ,1,0)

caret::confusionMatrix(reference = as.factor(testProbs$obs), 
                       data = as.factor(testProbs$predClass), 
                       positive = "1")
```

## ROC Curve
writing....
```{r}
ggplot(testProbs, aes(d = obs, m = pred)) + 
  geom_roc(n.cuts = 50, labels = FALSE, color = "#86BBD8") + 
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = "#2F4858") 
```

## AUC
```{r}
auc(testProbs$obs, testProbs$pred)
```


## Cross Validation
```{r}
#rm(calgary_slope.sf, flood.sf)
#gc()
ctrl <- trainControl(method = "cv", 
                     number = 100, 
                     savePredictions = TRUE,
                     returnData = FALSE)

cvdata <- fishnet_calgary %>% 
  as.data.frame() %>%
  dplyr::select(-objectid, -geometry, -ldscmetric, -uniqueID) %>%
  dplyr::mutate(inundation = as.factor(inundation),
                slope = as.factor(slope),
                impervious = as.factor(impervious))

cv_labels <- cvdata[,"inundation"]
cv_data <- cvdata[,-2]

cvFit <- caret::train(x=cv_data, y=cv_labels, 
               method="glm", family="binomial",
               trControl = ctrl, model = FALSE)

cvFit

```

```{r}
ggplot(as.data.frame(cvFit$resample), aes(Accuracy)) + 
  geom_histogram() +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Accuracy",
       y="Count")+
  plotTheme1()
```


# Predictions
```{r}
calgary_allPredictions <- 
  predict(cvFit, fishnet_calgary, type="prob")[,2]
  
fishnet_calgary <- 
  cbind(fishnet_calgary,calgary_allPredictions) 

fishnet_calgary1 <- fishnet_calgary %>%
  mutate(PredClass = ifelse(calgary_allPredictions >= 0.5, 1, 0))

fishnet_calgary1 <- fishnet_calgary1 %>%
  mutate(Correct = ifelse(PredClass == 1, "1", "0"),
         Incorrect = ifelse(PredClass != 1, "1", "0"))
ggplot() + 
    geom_sf(data= fishnet_calgary1, aes(fill=factor(ntile(allPredictions.1,5))), 
            colour=NA) +
    scale_fill_manual(values = c("#DEF5E5FF","#49C1ADFF","#357BA2FF","#3E356BFF","#0B0405FF"),
                      labels=as.character(quantile(fishnet_calgary1$allPredictions.1,
                                                 c(0,0.2,0.4,0.6,0.8),
                                                 na.rm=T)),
                      name="Predicted\nProbabilities(%)\n(Quintile\nBreaks)") +
  mapTheme1() +
   labs(title="Predicted Flooded Areas in Calgary")

ggplot() + 
    geom_sf(data= fishnet_calgary1, aes(fill=factor(ntile(PredClass,2))), 
            colour=NA) +
    scale_fill_manual(values = c("#DEF5E5FF","#49C1ADFF"),
                      labels=as.character(quantile(fishnet_calgary1$PredClass,
                                                 c(0,1),
                                                 na.rm=T)),
                      name="Predicted Outcome)") +
  mapTheme1() +
   labs(title="Predicted Flooded Areas in Calgary")

```

#Confusion Metrics -> Calgary
```{r}
fishnet_calgary1 %>%
  mutate(confResult=case_when(calgary_allPredictions < .50 & inundation==0 ~ "True_Negative",
                              calgary_allPredictions >= .50 & inundation==1 ~ "True_Positive",
                              calgary_allPredictions < .50 & inundation==1 ~ "False_Negative",
                              calgary_allPredictions >= .50 & inundation==0 ~ "False_Positive")) %>%
  ggplot()+
  geom_sf(aes(fill = confResult), color = "transparent")+
  scale_fill_manual(values = c("#DEF5E5FF","#49C1ADFF","#357BA2FF","#3E356BFF"),
                    name="Outcomes")+
  labs(title="Confusion Metrics For Calgary") +
  mapTheme1()
```

## Confusion Metrics -> Minneapolis
```{r}
fishnet_calgary1 %>%
  mutate(confResult=case_when(minneapolis_allPredictions < .50 & inundation==0 ~ "True_Negative",
                              minneapolis_allPredictions >= .50 & inundation==1 ~ "True_Positive",
                              minneapolis_allPredictions < .50 & inundation==1 ~ "False_Negative",
                              minneapolis_allPredictions >= .50 & inundation==0 ~ "False_Positive")) %>%
  ggplot()+
  geom_sf(aes(fill = confResult), color = "transparent")+
  scale_fill_manual(values = c("#DEF5E5FF","#49C1ADFF","#357BA2FF","#3E356BFF"),
                    name="Outcomes")+
  labs(title="Confusion Metrics For Calgary") +
  mapTheme1()
```


## Predictions for Minneapolis, MN
```{r}
minneapolis_allPredictions <- 
  predict(cvFit, fishnet_minneapolis, type="prob")[,2] 

minneapolis_pred <- 
  cbind(fishnet_minneapolis,minneapolis_allPredictions) %>% 
  mutate(minneapolis_allPredictions = round(minneapolis_allPredictions * 100))

ggplot() + 
  geom_sf(data=fishnet_minneapolis, aes(fill=factor(ntile(minneapolis_allPredictions,5))), 
          colour=NA) +
  scale_fill_manual(values = c("#DEF5E5FF","#49C1ADFF","#357BA2FF","#3E356BFF","#0B0405FF"),
                    labels=as.character(quantile(fishnet_minneapolis$minneapolis_allPredictions,
                                                 c(0.1,.2,.4,.6,.8),
                                                 na.rm=T)),
                    name="Predicted\nProbabilities(%)\n(Quintile\nBreaks)") +
  mapTheme1() +
  labs(title="Predicted Flooded Areas in Portland-Vancouver")
```

Spatial Cross Validation -> predicting policing lab? 

# Discussion & Conclusion 
blah blah blah


[1] https://community.fema.gov/ProtectiveActions/s/article/Flood-Impact#:~:text=Floods%20can%20cause%20power%2C%20water,problems%20including%20landslides%20and%20mudslides.
